Observed vs. Simulated Year Comparison

### 2022-01-11 03-post-process/compare-sim-to-obs.Rmd
Update more variable names
This time, done throughout all files

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O1_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-3 Maturity: Estimates")
ratio_plots(x, "Age-3 Maturity: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-3 Maturity"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O2_Rb[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-4 Maturity: Estimates")
ratio_plots(x, "Age-4 Maturity: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-4 Maturity"))
```

@@

```{r}
pop_ts_plots("^psi_O1_Rb[year,origin,pop]", origin = 1)
```

@@

```{r}
pop_ts_plots("^psi_O2_Rb[year,origin,pop]", origin = 1)
```

>>>>

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O1[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O1[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-3 Maturity: Estimates")
ratio_plots(x, "Age-3 Maturity: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-3 Maturity"))
```

@@

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("^psi_O2[year,origin,pop]", obs_y, sim_y, origin = 1, pop = j)),
  lapply(1:4, function(j) get_ratio("^psi_O2[year,origin,pop]", obs_y, sim_y, origin = 2, pop = j))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Age-4 Maturity: Estimates")
ratio_plots(x, "Age-4 Maturity: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "SW Juvenile", Type = "Age-4 Maturity"))
```

@@

```{r}
pop_ts_plots("^psi_O1[year,origin,pop]", origin = 1)
```

@@

```{r}
pop_ts_plots("^psi_O2[year,origin,pop]", origin = 1)
```
